\documentclass[a4paper,11pt] {report}
\usepackage{geometry}
\usepackage{fancyheadings}
\usepackage{advdate}
\usepackage{details}

\lhead{\Huge\bf \myname}
\chead{}
\rhead{GSTIN: \mygstin \\ \mymobile \\ \tiny{\mymail}}

\cfoot{}

\pagestyle{fancy}

\usepackage{color} 
\usepackage{setspace} 

\geometry{top=2cm, bottom=2cm,left=2.5cm, right=2.5cm}

\begin{document}
\vspace*{2cm}
To,\newline
The Assistant Commissioner- Goods and Services Tax,\newline
Division: Central Tax Rohini,\newline
7th floor, 11th Block, \newline
CGO Complex Lodhi Road, \newline
New Delhi-110003. 

Subject:- Request to accept ‘Letter of Undertaking’ of firm “\myfirm” (GSTN:\mygstin)

\bigbreak

Sir, \newline

I, \myname, R/o \underline{\myaddress}, sole Proprietor of firm
registered under my name, {\bf{\myfirm}} having Goods and Services Tax
Identification Number {\bf{\underline{\mygstin}}} request you to
please accept ‘Letter of Undertaking’ of “\myfirm” as my unit
satisfies all eligibility criteria for this. Documents attached
herewith for your perusal are:
\begin{enumerate}
\item GST Registration Certificate.
\item GST FORM RFD-11- in duplicate.
\item Annexure- Letter of Undertaking (LUT)- in duplicate.
\item ID proof of witnesses signing on LUT.
\item Self-Declaration.
\item My ID Proof (PAN and ID).
\item My Airtel broadband statement for Utility Bill.
\item Notarized, No Objection Certificate(NOC) from my landlord,
  allowing me to work from the rented space.
\end{enumerate} 
Thank you,

Kind Regards, \bigbreak \bigbreak

\myname

Date: \DayAfter[1]
\end{document}
